Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
minor fix

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system whilst remaining safe given a 
pre-selected time horizon; then, we verify its potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
to unfold the dynamics forward, instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. 
\todo{We need to mention the CEGIS architecture here. We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS.

@@

A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
\begin{align*}
\sum_{i=0}^{\infty}T^i  &= (I - T)^-1
\end{align*}
Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge

>>>>

We describe and evaluate two approaches for synthesising digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system whilst remaining safe given a 
pre-selected time horizon; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
to unfold the dynamics forward, instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. 
\todo{We need to mention the CEGIS architecture here. We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
We provide experimental results 
showing that both approaches are able to efficiently synthesise stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $\underline{x_{i}}=-1$ and 
$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS.

@@

A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
\begin{align*}
\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
\end{align*}
Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
